Stability and Performance of Coalitions of Prosumers Through Diversification in the Smart Grid

### 2016-02-17 review.tex
respond change

		\textbf{Answer :} In this work, the grid operator is only responsible for selecting the minimum production threshold $P^{MIN}$ and the reliability threshold $ \phi $ whom coalitions should comply with. Furthermore, the consumption production balance over the grid is not addressed here. We indeed focus on the formation of productive coalitions that propose some production capacity over a period of time. In a more complex and maybe more realistic framework, we could imagine that these parameters ($P^{MIN}$ and $ \phi $) are selected by some market process, or that the electricity price depends on the uncertainty of the production, such that power from unreliable coalitions is cheaper than power from reliable ones.

>>>>

		\textbf{Answer :} In this work, the grid operator is only responsible for selecting the minimum production threshold $P^{MIN}$ and the reliability threshold $ \phi $ whom coalitions should comply with. We agree that the terminology used could be misleading, so, as to avoid any confusion, we renamed this entity "market operator". Prosumers are grouped in coalitions managed by aggregators that whish to sell on the energy market. In order to do so, they have to respect the conditions fixed by the "market operator". The balance between production and consumption in the grid is not addressed here. However energy markets, as depicted in this work, could very well be some way, for the actual grid operator, of preserving this equilibrium. As to make sure that both the scenario and the limitations of our work are clear, we clarify these points in the begining of the introduction.
